Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-21 writing/DraftExposurePaper/DraftExposurePaper.Rmd
work on precip validation

```{r}
gauge <- read.csv("/Users/joshuaferreri/Documents/NWR_Alex_Rain.csv", header = TRUE)
nldas <- county_rain(counties = unique(gauge$fips),
                             start_year = 2010, end_year = 2010,
                             rain_limit = 0, dist_limit = 500,
                             days_include = c(-2, 0, 1))
nldas <- nldas %>%
        filter(storm_id == "Alex-2010")
gauge$fips <- as.character(gauge$fips)
compare_rain <- full_join(nldas, gauge, by = "fips")
#compare_rain <- full_join(nldas, gauge, by = "fips")
a <- ggplot(compare_rain, aes(rain_mm, tot_precip, color = fips)) + geom_point()
a
```

>>>>

```{r}
alex_gauge <- read.csv("/Users/joshuaferreri/Documents/NWR_Alex_Rain.csv", header = TRUE)
alex_nldas <- county_rain(counties = unique(gauge$fips),
                             start_year = 2010, end_year = 2010,
                             rain_limit = 0, dist_limit = 500,
                             days_include = c(-2, 0, 1))
alex_nldas <- alex_nldas %>%
        filter(storm_id == "Alex-2010")
alex_gauge$fips <- as.character(alex_gauge$fips)
compare_rain <- full_join(alex_nldas, alex_gauge, by = "fips")
#compare_rain <- left_join(alex_nldas, alex_gauge, by = "fips")
a <- ggplot(compare_rain, aes(rain_mm, tot_precip, color = fips)) + geom_point()
a
```
